---
title: \vspace{2.25in}Analysis of Airbnb Listings During the Coronavirus Pandemic
author: 
- "Prepared by:"
- Dazzelle Bagtas
- Kylie Wise
- Logan Hylton
- Braeden Obar
date: \vspace{2.5in} May 6, 2021
fontsize: 12pt
geometry: margin=1in
linkcolor: black
urlcolor: black
output: 
  pdf_document:
    toc_depth: 3
    number_sections: true
bibliography: references.bib 
nocite: '@*'
header-includes:
- \usepackage{setspace}
- \onehalfspacing
- \renewcommand{\and}{\\}
- \usepackage[nottoc]{tocbibind}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, highlight=FALSE, message=FALSE)
```

\pagenumbering{gobble}

\newpage 
\pagenumbering{roman} 

\tableofcontents 


\newpage

\renewcommand{\listtablename}{List of tables}
\listoftables

\renewcommand{\listfigurename}{List of figures}
\listoffigures


\newpage
\pagenumbering{arabic} 

# Executive summary {-}

This project investigates what characteristics are important in producing a high reservation rate for an Airbnb listing. This information is important considering that the Covid-19 pandemic has hurt the hospitality industry, and determining which factors are important in helping listings get reserved may provide guidance as to how Airbnb can assist hosts to continue receiving reservations and sustain their business. The data used for this analysis are listing information for Airbnbs in New York City from January 2020 to March 2021, which was obtained from Insideairbnb.com. The data includes information about listings such as their physical characteristics, corresponding host information, prices, and the days which they were reserved within a year. Through descriptive analysis, it was revealed that the number of reservations booked within a month increased during 2020. Additionally, the number of bookings within the first three months of 2021 was less than the first three months of 2020. Through predictive analysis, specifically random forest modeling, it was revealed that the most important variables that play a factor in customers' decision to reserve a listing are the total number of listings a host has, the number of people it accommodates, the minimum nights required to stay, whether the host is a superhost, and price. Our recommendations for Airbnb to help their hosts are to decrease host costs and provide real estate assistance.
 

\newpage
```{r, child='Deliverable1 final.Rmd'}

```

```{r, child='Deliverable2 final.Rmd'}

```

```{r, child='Deliverable3 final.Rmd'}

```
 
```{r, child='Deliverable4 final.Rmd'}

```

# Conclusions
Ultimately, through this analysis we were able to investigate which factors are important in resulting in high reservation rates for an Airbnb listing. We were able to find that the number of listings that a host has, the minimum number of nights for the booking, the number of guests it can accommodate, the minimum nights required to stay, and the price are all important factors. Given that the number of listings that a host has was the most important, this may signal that guests are looking for hosts with experience and expertise in running Airbnb listings as they are looking for safety and a reliable place to stay, specifically within the pandmeic. We also determined that certain favorable Airbnb description features have changed as a result of the pandemic. For example, we revealed an increase in listings using the word "space", which may indicate that hosts should include this within their descriptions to attract customers in the meantime. This information is valuable to Airbnb stakeholders and Airbnb itself in how they can change their business to focus more on marketing what the consumers value the most when selecting a listing. The Covid-19 pandemic has undoubtedly hurt the hospitality and lodging industry, and determining which factors are important in helping listings get reserved may provide guidance as to how Airbnb can assist hosts to continue receiving reservations and sustain their business. 

# Recommendations

1. **Reduce Host Costs** 
\newline
Given that price appears to be an important factor in whether customers choose to reserve a listing or not, one recommendation is that Airbnb help subsidize hosts' costs of running Airbnbs to possibly provide leeway for hosts to decrease their prices and attract more customers. For example, Airbnb may decrease the rates of their hosts' service fees or possibly provide stipends so that hosts may better afford home upgrades or cleaning supplies. A drawback of this is the cost that Airbnb would have to take on. This would be extra expenses or reduced revenue on their part; however, if the decrease in host costs increases their reservation rates enough, the revenue they receive may be enough to also offset the increased expenses for Airbnb.
\newline

2. **Provide Real Estate Assistance**
\newline
Additionally, given that the total number of listings that a host has is also important in factor in whether a customer reserves a listing or not, it may be useful for Airbnb to provide additional resources of how hosts may acquire new properties to lease. This may include providing databases of properties that are available and guiding hosts through the process of acquiring them. The drawback is that this would require additional skills within Airbnb to create such a resource. Additionally, the success of such a resource would vary depending on location and how many properties are available in general.
\newline

3. **Track and Publish Description Changes and Trends** 
\newline
Tracking and publishing words that are frequently used in successful descriptions can give renters a better idea of which properties to invest in and how best to advertise to consumers. It also may be beneficial for Airbnb to track these trends in order to better understand consumer behavior to make more-informed business decisions that put the desires and preferences of the consumers first. One drawback of this suggestion is that if renters get access to this information, it may be tempting to put in these key words even if the property does not actually include these amenities or features.  
\newline

\newpage
# References {-}
<div id="refs"></div>

\newpage
\renewcommand\thepage{A-\arabic{page}}
\setcounter{page}{1}

```{r, child='AppendixA.Rmd'}
```

\newpage
\renewcommand\thepage{B-\arabic{page}}
\setcounter{page}{1}

```{r, child='AppendixB.Rmd'}
```

\newpage
\renewcommand\thepage{C-\arabic{page}}
\setcounter{page}{1}

```{r, child='AppendixC.Rmd'}
```

\newpage
\renewcommand\thepage{D-\arabic{page}}
\setcounter{page}{1}

```{r, child='AppendixD.Rmd'}
```
